### 2017-01-04 R/tutorial.Rmd
Update to tutorial

```{r libs2, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
library("devtools")
install_github(repo = "syounkin/ITHIM")
library("ITHIM")
```

@@

>>>>

```{r libs2, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}
library("devtools")
install_github(repo = "syounkin/ITHIM", ref = "devel")
library("ITHIM")
```

### Step-by-step

@@

```{r class, eval = TRUE, dev=c('pdf', 'png'), fig.width = fig.width, fig.asp = 1/phi, warning = FALSE, message = FALSE, echo = TRUE}

```
